%%%%%%%%%%%%%%%%%%%%%%

\chapter{Project development}
    
    \section{Implementation choices}
    
    
    
    \section{Dataset}
    
    For the experiments we use two different kind of dataset, a small one so we can easily brute-force the real indices and compare the relative errors, and a big one in order to benchmark the performance of the different approach.
    
    \paragraph*{NetInf} This graph represents the flow of information on the web among blogs and news websites. The graph was computed by the \textit{NetInf} approach, as part of the \textit{SNAP} project~\cite{netinf}, by tracking cascades of information diffusion to reconstruct ``who copies who'' relationships.
    
    \begin{itemize}
    	\item $V$ is the set of blog or news website, $|V| = 854$.
    	\item $E$, each website is connected to those who frequently copy their content, $|E| = 3824$.
    	\item $\Sigma$ is the set of ranking class of websites ($0$ top $4\%$, $1$ next $15\%$, $2$ next $30\%$, $3$ last $51\%$), $|\Sigma| = 4$.
    	\item $L$, each website is labeled according to its importance, using Amazon's Alexa ranking.
    \end{itemize}

    % Each node represents a blog or news website, and a website is connected to those who frequently copy their content. The graph contains 854 nodes and 3824 edges. We labelled websites according to their importance, using Amazon's Alexa ranking~\cite{alexarank}: the labels correspond to respectively the websites ranked in the top $4\%$, the following $15\%$, the following $30\%$, and the remaining $51\%$ (i.e. $|\Sigma|=4$). 
    
    \textsl{Considered query:} compute the similarity of two websites $a$ and $b$ or two sets of websites.
    
    \paragraph*{IMDb} In this graph, taken from the \textit{Internet Movie Database} we have:
    
    \begin{itemize}
    	\item $V$ is the set of all movies in \textit{IMDb},  $|V| = 1\,060\,209$.
		\item $E$, two movies are connected if their casts share at least one actor, $|E| = 288\,008\,472$.
		\item $\Sigma$ is the set of movies genre, $|\Sigma| = 36$.
		\item $L$, each movie is labeled with its principal genre.
    \end{itemize}
    
    % , nodes correspond to movies, and there is a link between two movies if their casts share at least one actor. The graph contains 1\,060\,209 movies (nodes) and 288\,008\,472 edges. Each movie is labeled with one of $|\Sigma|=36$ genres. 
    
    \textsl{Considered query:} similarity of actors' ego networks. Given two actors $a$ and $b$, let $A$ and $B$ be their ego-networks, i.e., the sets of nodes corresponding to movies in which respectively $a$ and $b$ starred, compute the similarity of $A$ and $B$.
    %Compute $BC(A,B)$, $J(A,B)$, $FJ(A,B)$, and random $q$-walks.
    
    \section{Experimental results}

    We describe the experimental evaluation for our approach. Our computing platform is a machine with Intel(R) Xeon(R) CPU E5-2620 v3 at 2.40GHz, 24 virtual cores, 128 Gb RAM, running Ubuntu Linux version 4.4.0-22-generic. Code written in C++ and compiled with g++ version 5.4.1 with OpenMP 4.5. 
    
	TODO 